The investment strategy based on behavior of artificial earthworm for use in algotrading

### 2014-05-07 Article/Article20140406Granada/LatexArt/article_main.tex
word->element

It is assumed that the time series is Si where $i = 1, 2, ...,$ and each word is a vector $S_i = (O_i, H_i, L_i, C_i)$ called candle consisting of  four values: Open, High, Low and Close of time between the time t and t +1. I is the final index of word which is the last word in time series that was taken under consideration.\\

>>>>

It is assumed that the time series is Si where $i = 1, 2, ...,$ and each element is a vector $S_i = (O_i, H_i, L_i, C_i)$ called candle consisting of four values: Open, High, Low and Close of time between the time $t$ and $t+1$. I is the final index of word which is the last word in time series that was taken under consideration.\\
